Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-22 manuscripts/reply/reply-abstract.tex
More editing of reply ms.

% Biogeographers frequently seek to explain population and species
% differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred at the same
time can be a potentially persuasive argument that the populations were
affected by the same geographic event.
% Unfortunately, estimating divergence times precisely when one lacks
% precise information about the rate of molecular evolution is a notoriously
% difficult problem in evolutionary biology.
% \citet{Huang2011} introduced an approximate-Bayesian approach, \msb, for
% estimating the probabilities of models in which multiple sets of taxa diverge
% at the same time.
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.
Recently, \citet{Oaks2012} used an approximate-Bayesian model choice method
(\msb) to estimate the support for such a pattern of divergences across 22
pairs of taxa from the Philippines.
They also studied the behavior of \msb using computer simulations.
\citet{Oaks2012} found the method was very sensitive to prior assumptions and
had low power to detect variation in divergence times.
These results were not surprising in light of a rich statistical literature
showing that the marginal likelihood of a model is sensitive to the
use of vague priors.
Because this sensitivity to prior assumptions affects the crucial insights 
that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
that users of the approach should carefully assess the robustness of their 
conclusions to different priors.
According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
was due to excessively broad priors on divergence times leading to 
inadequate numbers of simulation replicates.
They proposed a model-averaging approach that uses narrow, empirically
informed uniform priors.
Here we demonstrate that the approach of \citet{Hickerson2013} is
dangerous in the sense that the empirically-derived priors often
exclude from consideration the true values of the models' parameters.
On a more fundamental level, we question the value of adopting an empirical
Bayesian stance for this model-choice problem, because it can mislead model
posterior probabilities, which are inherently measures of belief in the
models after prior knowledge is updated by the data.
The robust Bayesian approach of conducting analyses under a variety
of priors can reveal prior sensitivity and communicate which assumptions
underlie model inference.
Furthermore, simulations provide insight into the temporal resolution of the
method, which helps guide interpretation of results.

>>>>

% Biogeographers frequently seek to explain population and species
% differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred at the same
time can be a potentially persuasive argument that the populations were
affected by the same geographic event.
% Unfortunately, estimating divergence times precisely when one lacks
% precise information about the rate of molecular evolution is a notoriously
% difficult problem in evolutionary biology.
% \citet{Huang2011} introduced an approximate-Bayesian approach, \msb, for
% estimating the probabilities of models in which multiple sets of taxa diverge
% at the same time.
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.
Recently, \citet{Oaks2012} used an approximate-Bayesian model choice method
(\msb) to estimate the support for such a pattern of divergences across 22
pairs of taxa from the Philippines.
They also studied the behavior of \msb using computer simulations.
\citet{Oaks2012} found the method was very sensitive to prior assumptions and
had low power to detect variation in divergence times.
These results were not surprising in light of a rich statistical literature
showing that the marginal likelihood of a model is sensitive to the
use of vague priors.
Because this sensitivity to prior assumptions affects the crucial insights 
that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
that users of the approach should carefully assess the robustness of their 
conclusions to different priors.
According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
was due to excessively broad priors on divergence times leading to 
inadequate numbers of simulation replicates.
They proposed a model-averaging approach that uses narrow, empirically
informed uniform priors.
Here we demonstrate that the approach of \citet{Hickerson2013} will often
incorrectly support shared divergence events and is dangerous in the sense that
the empirically-derived priors often exclude from consideration the true values
of the models' parameters.
On a more fundamental level, we question the value of adopting an empirical
Bayesian stance for this model-choice problem.
% , because it can mislead model
% posterior probabilities, which are inherently measures of belief in the models
% after prior knowledge is updated by the data.
The robust Bayesian approach of conducting analyses under a variety of priors
can reveal prior sensitivity and communicate which assumptions underlie model
inference.
Furthermore, simulations provide insight into the temporal resolution of the
method, which helps guide interpretation of results.
Fortunately, as predicted by fundamental principles of Bayesian model choice,
more appropriate priors on the model's parameters increase the method's
robustness and power to detect temporal variation in divergences
\citep{Oaks2014dpp}.

### 2014-07-22 manuscripts/reply/reply-main.tex
More editing of reply ms.

\change{
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice.
}
We then evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
We avoid this error, but still find their approach will often spuriously
support clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
We also explore the predictions of the causes of the bias proposed by
\citet{Oaks2012} and \citet{Hickerson2013}.
We show the primary cause of the method's tendency to incorrectly infer shared
divergences is the disparity in marginal likelihoods across divergence models
imposed by the uniform priors on divergence times.
We also show that sampling error is not a major contributer to the problem.
Fortunately, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without inhibiting the marginal likelihoods of models with
more divergence-time parameters, which increases the method's robustness and
power to detect temporal variation in divergences.

@@

\begin{linenomath}
Whereas empirical Bayesian approaches can provide powerful methods for
parameter estimation, a theoretical justification for empirical Bayesian
approaches to model choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and
the data are strongly informative relative to the prior, the values of the
parameters that maximize the posterior distribution will be relatively robust
to prior choice, even if the posterior distribution is technically incorrect
due to using the data to inform the priors.
By giving the data more weight relative to the prior, the goal of empirical
Bayesian parameter estimation is to estimate a distribution that will be peaked
near the true value(s) of the model's parameter(s).
% This is why empirical Bayes can work well for estimating the values of model
% parameters.
\end{linenomath}

% Unlike parameter estimates, posterior probabilities represent a summary of the
% entire posterior distribution.
% Thus, given that empirical Bayesian posterior distributions are not accurate,
% there is no guarantee regarding the accuracy of probabilities summarized from
% them.

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model that
updates the prior to yield the model's posterior probability.
The integral over the entire parameter space of the likelihood weighted by the
prior probability density is no longer a normalizing constant, but rather is
what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than parameter estimation.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
% There is no such justification for empirical Bayesian model choice, because
% there are no true values for the model probabilities being estimated.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.
This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
% In some simple situations we might suspect that one model is correct and the
% rest are wrong, but in most applications, we know that all the models under
% consideration are oversimplifications of reality.

@@

For our re-analyses of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's support of models with less parameter space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

\change{
When using uniformly distributed priors, the alternative to priors that reflect
prior uncertainty is to risk excluding the true values one seeks to estimate,
as shown above.
Fortunately, continuous distributions more appropriate as priors for positive
real-valued parameters have been shown to greatly reduce spurious support for
clustered divergence models while allowing prior uncertainty to be accommodated
\citep{Oaks2014dpp}.
}

@@

\section{General thoughts on the model of \texttt{msBayes}}
Our findings are not surprising in light of the difficult inference problem
with which \msb is faced.
% To get a sense of the difficulty of this problem, we tally up all the free
% parameters of the \msb model as applied to the dataset of \citet{Oaks2012}.
% Under the simplest model in \msb (i.e., assuming no migration and no
% intra-locus recombination), the number of parameters for each taxon pair
% include:
% The population sizes of the ancestral and descendant populations
% (\ancestralTheta{}, \descendantTheta{1}{}, \descendantTheta{2}{}),
% the magnitude of population contraction in each of the descendant
% populations (\bottleScalar{1}{} and \bottleScalar{2}{}), the
% timing of these contractions (\bottleTime{}), and the $N-1$ node heights
% (coalescent times) of the gene tree that gave rise to the $N$ gene
% copies sampled from both populations.
% Lastly, there are between one and 22 divergence time parameters \divt{} in
% the vector \divtvector.
When applying the simplest model in \msb (i.e., assuming no migration and no
intra-locus recombination) to the dataset of \citet{Oaks2012} with 22 taxon
pairs, there are 581--602 free parameters that model highly stochastic
coalescent and mutational processes.
Furthermore, under this rich stochastic model, the method is estimating the
probability of 1002 divergence models \citep[i.e., the number of integer
partitions of $Y=22$;][]{Oaks2012}.
Furthermore, all the information in the sequence alignment of each taxon pair
is distilled into four summary statistics:
$\pi$ \citep{Tajima1983}, $\theta_W$ \citep{Watterson1975}, $\pi_{net}$
\citep{Takahata1985}, and $SD(\pi-\theta_W)$ \citep{Tajima1989}.
That gives us a total of 88 summary statistics (four from each of the 22 taxon
pairs), which contain minimal information about many of the $\approx 600$
parameters in the model.
More summary statistics can be used in \msb, but most are highly correlated
with the four default statistics, and thus contribute little additional
information about the parameters from the sequence data.
The large number of parameters and divergence models relative to the amount of
information in the data is undoubtedly a key reason the method lacks robustness
to prior conditions.
Robustness is an important characteristic of a method to gauge its
applicability to real-world data, because we know the model and priors will be
wrong to some degree.

@@

The recommendations of \citet{Oaks2012} for mitigating the lack of robustness
of \msb are similar to those of \citet{Hickerson2013}, but avoid the
need for imposing an additional dimension of model choice.
\citet{Oaks2012} suggest that uniform priors may not be appropriate for many
parameters of the \msb model, and recommend the use of probability
distributions from the exponential family.
If we look at the prior distribution on divergence-time parameters imposed by
the model-averaging approach of \citet{Hickerson2013} we see it is a mixture of
overlapping uniforms with lower limits of zero (Figure~S\ref{figMCTauPrior}).
This looks very much like an exponential distribution, except that in any state
of the model, all the divergence-time parameters are restricted to the hard
bounds of one of the uniform distributions.
Thus, it seems more appropriate to simply place a gamma prior (the exponential
being a special case of the gamma) on divergence times.
This would capture the prior uncertainty that \citet{Hickerson2013} are
suggesting for divergence times (Figure~S\ref{figMCTauPrior}) while avoiding
costly model-averaging and the constraint that all divergence times must fall
within the hard bounds of the current model state.
It also would allow an investigator to place the majority of the prior density
in regions of parameter space they believe, \emph{a priori}, are most
plausible, but still capture uncertainty in the tails of distributions with low
density.
Indeed, \citet{Oaks2014dpp} has shown that the use of more flexible
distributions in place of uniform priors improves the power of the method to
detect temporal variation in divergences and reduces the bias toward models of
clustered divergences.

>>>>

\change{
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice.
}
We then evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
We avoid this error, but still find their approach will often spuriously
support clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
We also explore the predictions of the potential causes of the bias proposed by
\citet{Oaks2012} and \citet{Hickerson2013}.
We show the primary cause of the method's tendency to incorrectly infer shared
divergences is the disparity in marginal likelihoods across divergence models
imposed by the uniform priors on divergence times.
We also show that sampling error is not a major contributer to the problem.
Fortunately, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without inhibiting the marginal likelihoods of models with
more divergence-time parameters, which increases the method's robustness and
power to detect temporal variation in divergences.

@@

\begin{linenomath}
Whereas empirical Bayesian approaches can provide powerful methods for
parameter estimation, a theoretical justification for empirical Bayesian
approaches to model choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
\end{linenomath}

In Equation \ref{eq:bayesrule}, we see that the posterior density of any state
$\myTheta{}$ of the model, is the prior density updated by the probability of
the data given $\myTheta{}$ (the likelihood of $\myTheta{}$).
The integral over the entire parameter space of the model only appears as a
normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data and the data are strongly informative
relative to the prior, the values of the parameters that maximize the posterior
distribution will be relatively robust to prior choice, even if the posterior
is technically incorrect due to using the data to inform the priors.
However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model that
updates the prior to yield the model's posterior probability.
The integral over the entire parameter space of the likelihood weighted by the
prior probability density is no longer a normalizing constant, but rather is
what informs the posterior probability of the model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than parameter estimation.
Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.

The justification for an empirical Bayesian approach to parameter estimation is
that giving the data more weight relative to the prior (i.e., using the data
twice), will often shift the peak of the estimated distribution nearer to the
true value(s) of the model's parameter(s).
However, there is often no such justification for model selection, because
unlike model parameters, the posterior probabilities of candidate models often
have no clear true values.
% There is no such justification for empirical Bayesian model choice, because
% there are no true values for the model probabilities being estimated.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.
This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.

@@

For our re-analyses of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics after standardizing the
statistics using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors exclude
most, if not all, of the divergence times of the Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's tendency to support models with less parameter
space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

\change{
When using uniformly distributed priors, the alternative to priors that reflect
prior uncertainty is to risk excluding the true values one seeks to estimate.
Fortunately, continuous distributions more appropriate as priors for positive
real-valued parameters have been shown to greatly reduce spurious support for
clustered divergence models while allowing prior uncertainty to be accommodated
\citep{Oaks2014dpp}.
}

@@

% \section{General thoughts on the model of \texttt{msBayes}}
\section{A difficult inference problem}
Our findings are not surprising in light of the difficult inference problem
with which \msb is faced.
% To get a sense of the difficulty of this problem, we tally up all the free
% parameters of the \msb model as applied to the dataset of \citet{Oaks2012}.
% Under the simplest model in \msb (i.e., assuming no migration and no
% intra-locus recombination), the number of parameters for each taxon pair
% include:
% The population sizes of the ancestral and descendant populations
% (\ancestralTheta{}, \descendantTheta{1}{}, \descendantTheta{2}{}),
% the magnitude of population contraction in each of the descendant
% populations (\bottleScalar{1}{} and \bottleScalar{2}{}), the
% timing of these contractions (\bottleTime{}), and the $N-1$ node heights
% (coalescent times) of the gene tree that gave rise to the $N$ gene
% copies sampled from both populations.
% Lastly, there are between one and 22 divergence time parameters \divt{} in
% the vector \divtvector.
When applying the simplest model in \msb (i.e., assuming no migration and no
intra-locus recombination) to the dataset of \citet{Oaks2012} with 22 taxon
pairs, there are 581--602 free parameters that model highly stochastic
coalescent and mutational processes.
Furthermore, under this rich stochastic model, the method is estimating the
probability of 1002 divergence models \citep[i.e., the number of integer
partitions of $Y=22$;][]{Oaks2012}.
Furthermore, all the information in the sequence alignment of each taxon pair
is distilled into four summary statistics:
$\pi$ \citep{Tajima1983}, $\theta_W$ \citep{Watterson1975}, $\pi_{net}$
\citep{Takahata1985}, and $SD(\pi-\theta_W)$ \citep{Tajima1989}.
That gives us a total of 88 summary statistics (four from each of the 22 taxon
pairs), which contain minimal information about many of the $\approx 600$
parameters in the model.
More summary statistics can be used in \msb, but most are highly correlated
with the four default statistics, and thus contribute little additional
information about the parameters from the sequence data.
The large number of parameters and divergence models relative to the amount of
information in the data is undoubtedly a key reason the method lacks robustness
to prior conditions.
% Robustness is an important characteristic of a method to gauge its
% applicability to real-world data, because we know the model and priors will be
% wrong to some degree.

@@

The recommendations of \citet{Oaks2012} for mitigating the lack of robustness
of \msb are similar to those of \citet{Hickerson2013}, but avoid the
need for imposing an additional dimension of model choice.
\citet{Oaks2012} suggest that uniform priors may not be appropriate for many
parameters of the \msb model, and recommend the use of probability
distributions from the exponential family.
If we look at the prior distribution on divergence-time parameters imposed by
the model-averaging approach of \citet{Hickerson2013} we see it is a mixture of
overlapping uniforms with lower limits of zero (Figure~S\ref{figMCTauPrior}).
This looks very much like an exponential distribution, except that in any state
of the model, all the divergence-time parameters are restricted to the hard
bounds of one of the uniform distributions.
Thus, it seems more appropriate to simply place a gamma prior (the exponential
being a special case of the gamma) on divergence times.
This would capture the prior uncertainty that \citet{Hickerson2013} are
suggesting for divergence times (Figure~S\ref{figMCTauPrior}) while avoiding
costly model-averaging and the constraint that all divergence times must fall
within the hard bounds of the current model state.
It also would allow an investigator to place the majority of the prior density
in regions of parameter space they believe, \emph{a priori}, are most
plausible, but still capture uncertainty in the tails of distributions with low
density.
Indeed, \citet{Oaks2014dpp} has shown that the use of more flexible
distributions in place of uniform priors improves the power of the method to
detect temporal variation in divergences and reduces incorrect support for
clustered divergences.
